---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# evmr

<!-- badges: start -->
<!-- badges: end -->

`evmr` is an R package for **extreme value modeling for r-largest order statistics**.

The package provides tools for modeling environmental and climate extremes using r-largest order statistics. It aims to support parameter estimation, return level estimation, and model diagnostics for extreme value distributions commonly used in hydrology, climatology, and environmental sciences.

## Features

The `evmr` package provides a unified framework for extreme value analysis based on r-largest order statistics.

Key features include:

- Parameter estimation for extreme value models
- Return level estimation for extreme events
- Model diagnostics and goodness-of-fit assessment
- Applications to climate and hydrological extremes

## Installation

You can install the development version of `evmr` from GitHub:

```r
# install.packages("remotes")
remotes::install_github("your_github_id/evmr")
```

Replace `"your_github_id"` with your GitHub username.

## Example

This example shows how to load the package.

```{r example}
library(evmr)
```

Future versions of the package will include functions for fitting extreme value models and estimating return levels using r-largest order statistics.

## Applications

The `evmr` package can be used for analyzing extreme events in areas such as:

- Hydrology (e.g., flood frequency analysis)
- Climatology (e.g., extreme temperature and precipitation)
- Environmental risk assessment
- Infrastructure design based on extreme events

## Development

`evmr` is currently under active development. Additional functionality and examples will be added in future releases.
